\input{include/assets/figures/streamer}
The Streamer tool corresponds to the data-synthesis stage, which means that it
is responsible for synthesizing power and temperature data using reference data
as a material for the synthesis; see the module labeled ``Streamer'' in
\fref{methodology}. The structure of the tool is laid out in \fref{streamer}.

Given an arrival pattern and a set of workload patterns, Streamer proceeds as
follows. The arrival pattern is processed as it was described in \sref{traffic},
which results in an adequately configured multifractal wavelet model
\cite{riedi1999}. The model is then used to generate a stream of arrival times.
At the same time, the workload patterns are used to construct a stream of
workloads, which was explained in \sref{workload}. The rest follows
\sref{composition}. Namely, the two stream are fused into a stream of jobs,
which is subsequently handled by a scheduling policy; in \fref{streamer}, this
policy is a part of the Main module. As the incoming jobs are being scheduled,
the power profile of the system under consideration is being constructed. The
power profile is piped into a temperature simulator (to be discussed below),
which delivers a temperature profile. The continuity of the process is worth
noting: just as with arrival and workload patterns, power and temperature can be
viewed as infinite streams of data. The synthesized data (power and temperature)
can be fed back to the scheduler and/or stored for later usage. In the latter
case, similar to reference data, the output is an SQLite database.

Let us now outline how temperature simulation is undertaken inside Streamer. The
simulation is based on the popular thermal \sc{RC} model. In this paradigm, a
so-called thermal \sc{RC} circuit representing the system at hand is constructed
and then used to analyze the thermal behavior of the system. The analysis boils
down to solving a system of differential equations, which can be done using
different integration techniques. In our case, the solution is based on a solver
leveraging exponential integrators \cite{hochbruck2010, ukhov2012}. The
construction of thermal circuits is outsourced to either HotSpot
\cite{skadron2004} or \sc{3D-ICE} \cite{sridhar2010} (in \fref{streamer}, the
latter is illustrated). Both simulators are based on the thermal \sc{RC} model,
and we extract the circuits that they build,\footnote{HotSpot has two models:
block and grid. We extract the circuits produced by the former.} which results
in a unified interface for working with the two alternatives.

To summarize this subsection, the Streamer tool produces streams of power and
temperature data, and this procedure closely follows the ideas presented in
\sref{methodology}. Our temperature simulation is based on the thermal \sc{RC}
model, in which thermal circuits are constructed by either HotSpot or
\sc{3D-ICE}.
