As described in \sref{problem-formulation}, the system at hand serves a stream
of jobs, which can be also viewed as user requests. The foremost component of
our methodology is then a traffic model, describing \emph{how} or, rather,
\emph{when} jobs arrive. This model should satisfy a number of requirements in
order to be practically useful. First of all, the model should be able to
capture the idiosyncrasies present in real traffic as it establishes a
foundation for the subsequent generation of power and temperature traces
(discussed in \sref{composition}). Second, it should be straightforward to
configure the model given a dataset of traffic data (a sequence of arrival times
of jobs) serving as a reference. Let us unfold the second requirement first.

The required ability to absorb reference data acknowledges the importance of the
information that is at our disposal due to monitoring and logging mechanisms
ubiquitously deployed nowadays (consider, for instance, log files of web
servers). In \fref{methodology}, such mechanisms are represented by a set of
modules labeled ``Logger.'' The corresponding data are assumed to be stored in a
repository, which is accessible for the later usage taking place in the module
labeled ``Streamer'' (to be discussed shortly). Such a repository could be a
community effort providing traffic data for research undertakings.

Monitoring and logging mechanisms, which are a natural source of traffic
patterns, are outside of the scope of this work. We only note that reference
traffic data should be collected in an environment similar to the one in which
the system at hand is supposed to function. For a better intuition about and a
good example of traffic data, the interested reader is referred to a publicly
available dataset \cite{google} containing traffic data of a large computer
cluster over a month period. The dataset was published for research purposes by
Google in 2011; it will be discussed further in \sref{experimental-results}. Let
us now move on to the analysis and synthesis of a chosen traffic pattern.

The seminal work in \cite{leland1994} and subsequent studies have shown that
network traffic exhibits fractal properties such as burstiness, self-similarity,
and long-range dependence, which is very much unlike traditional telephone
traffic. It is well known that traffic models based on the Poisson process
\cite{lifshits2014} are unable to express any of the above properties and,
therefore, drastically departure from reality when it comes to modeling network
traffic. A step in the right direction is to consider the fractional Gaussian
noise \cite{lifshits2014}, which is a self-similar stochastic process. However,
the process is inconvenient to work with from the perspective of a computer
simulator. More concretely, the noise is suited for modeling arrivals per unit
of time but not arrival or inter-arrival times, which are what is typically
needed for simulation. Moreover, even with a proper rescaling and shift, the
process can still take negative values, which is unrealistic. Finally, the
fractional Gaussian noise is a monofractal process; however, real traffic data
often have multifractal structures.

In order to address the aforementioned concerns and enable the generation of
arrival streams exhibiting fractal properties, our methodology employs the
multifractal wavelet model proposed in \cite{riedi1999}, characterizing
positive-valued data with long-range-dependent correlations. In brief, we take a
reference time series of arrival times, analyze it by means of the discrete
wavelet transform based on Haar wavelets, and construct a certain representation
of the data, which can then be used for generating random time series matching
the fractal properties of the original one. Hence, the model gets automatically
tailored to the traffic pattern of the particular problem at hand.

To sum up, we now have a dataset of reference arrival times and a versatile
technique for analyzing them and generating similar arrival streams. The
technique is capable of capturing the properties that are commonly present in
real traffic such as burstiness, self-similarity, and long-range dependence.
